### 2024-05-23 draft_jss/draft_jss.Rmd
update results after BH review

```{r fig.cap="Forecast"}
dfOutcome %>%
  mutate(pred = vec_pred) %>%
  na.omit() %>%
  ggplot(mapping = aes(x = outcomeDate)) +
  geom_line(mapping = aes(y = outcome,
                          color = "observed")) +
  geom_line(mapping = aes(y = pred,
                          color = "forecast")) +
  geom_vline(mapping = aes(color = "train-test sets",
                           xintercept = traintest_date)) +
  scale_color_manual(values = c("#3772ff", "#080708", "#df2935")) +
  theme_minimal() +
  labs(color = "", x = "Date", y = "Hospitalizations")
```

@@

```{r figForecastDerivvsRaw, fig.cap="Covid-19 hospitalizations forecast. The model is either trained to forecast the number of hospitalizations (denoted Raw) or the variation of the hospitalizations compared to current level of hospitalisation (denoted Variation)"}
## Fit reservoir on outcome variation instead of raw outcome
fit2 <- reservoirnet::reservoirR_fit(node = model,
                                     X = lsdf$xTrain,
                                     Y = lsdf$yTrain_variation,
                                     warmup = 30,
                                     reset = TRUE)
## Get the forecast on the test set
vec_pred2_variation <- reservoirnet::predict_seq(node = fit2$fit,
                                                 X = lsdf$xTest,
                                                 reset = TRUE)
## Transform the outome variation forecast into hospitalisation forecast
vec_pred2 <- vec_pred2_variation + xTest$hosp
## Plot the results
dfOutcome %>%
  mutate(Raw = vec_pred,
         Variation = vec_pred2) %>%
  tidyr::pivot_longer(cols = c(Raw, Variation),
                      names_to = "Outcome_type",
                      values_to = "Forecast") %>%
  na.omit() %>%
  ggplot(mapping = aes(x = outcomeDate)) +
  geom_line(mapping = aes(y = outcome,
                          color = "observed")) +
  geom_line(mapping = aes(y = Forecast,
                          color = "Forecast")) +
  geom_vline(mapping = aes(color = "train-test sets",
                           xintercept = traintest_date)) +
  facet_wrap(Outcome_type ~ .,
             labeller = label_bquote(cols = "Outcome" : .(Outcome_type))) +
  scale_color_manual(values = c("#3772ff", "#080708", "#df2935")) +
  theme_minimal() +
  labs(color = "", x = "Date", y = "Hospitalizations")
```

>>>>

```{r fig.cap="Forecast", fig.height=4, fig.width=7}
dfOutcome %>%
  mutate(pred = vec_pred) %>%
  na.omit() %>%
  ggplot(mapping = aes(x = outcomeDate)) +
  geom_line(mapping = aes(y = outcome,
                          color = "observed")) +
  geom_line(mapping = aes(y = pred,
                          color = "forecast")) +
  annotate("rect",
           xmin = traintest_date,
           xmax = max(dfOutcome$outcomeDate, na.rm = T),
           ymin = 0,
           ymax = max(dfOutcome$outcome, na.rm = T)*1.1, 
           alpha = .2) +
  annotate("text", label = "Test set", x = as.Date("2022-08-01"), y = 2200, size = 7) +
  annotate("text", label = "Train set", x = as.Date("2021-03-01"), y = 2200, size = 7) +
  scale_color_manual(values = c("#3772ff", "#080708")) +
  theme_minimal() +
  labs(color = "", x = "Date", y = "Hospitalizations")
```

@@

```{r figForecastDerivvsRaw, fig.cap="Covid-19 hospitalizations forecast. The model is either trained to forecast the number of hospitalizations (denoted Raw) or the variation of the hospitalizations compared to current level of hospitalisation (denoted Variation)", fig.height=4, fig.width=7}
## Fit reservoir on outcome variation instead of raw outcome
fit2 <- reservoirnet::reservoirR_fit(node = model,
                                     X = lsdf$xTrain,
                                     Y = lsdf$yTrain_variation,
                                     warmup = 30,
                                     reset = TRUE)
## Get the forecast on the test set
vec_pred2_variation <- reservoirnet::predict_seq(node = fit2$fit,
                                                 X = lsdf$xTest,
                                                 reset = TRUE)
## Transform the outome variation forecast into hospitalisation forecast
vec_pred2 <- vec_pred2_variation + xTest$hosp
## Plot the results
dfOutcome %>%
  mutate(Raw = vec_pred,
         Variation = vec_pred2) %>%
  tidyr::pivot_longer(cols = c(Raw, Variation),
                      names_to = "Outcome_type",
                      values_to = "Forecast") %>%
  na.omit() %>%
  ggplot(mapping = aes(x = outcomeDate)) +
  geom_line(mapping = aes(y = outcome,
                          color = "observed")) +
  geom_line(mapping = aes(y = Forecast,
                          color = "Forecast")) +
  annotate("rect",
           xmin = traintest_date,
           xmax = max(dfOutcome$outcomeDate, na.rm = T),
           ymin = 0,
           ymax = max(dfOutcome$outcome, na.rm = T)*1.1, 
           alpha = .2) +
  annotate("text", label = "Test set", x = as.Date("2022-08-01"), y = 2200, size = 5) +
  annotate("text", label = "Train set", x = as.Date("2021-03-01"), y = 2200, size = 5) +
  facet_wrap(Outcome_type ~ .,
             labeller = label_bquote(cols = "Outcome" : .(Outcome_type))) +
  scale_color_manual(values = c("#3772ff", "#080708")) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  labs(color = "", x = "Date", y = "Hospitalizations")
```
